---
title: "BPA calculation of BMD and overall uncertainty"
author: "Ullrika Sahlin"
date: "`r Sys.Date()`"

params: 
  hocs: c('immunotox','metabolic','neurotox','repro','carcino')
  probmassoutside: 0.001
  origALI: FALSE
  fit_distributions: FALSE
  Q1_ALI: c(66,66)
  SADEP: FALSE
  usesavedoutputs: TRUE
  figdir: fig_linearpool
output:
  html_document:
    toc: yes
    df_print: paged
    self_contained: true
---

```{r setup2, include=FALSE}
hocs <- params$hocs
probmassoutside <- params$probmassoutside
origALI <- params$origALI
fit_distributions <- params$fit_distributions
Q1_ALI = params$Q1_ALI

usesavedoutputs = params$usesavedoutputs
SADEP = params$SADEP

knitr::opts_chunk$set(dev = c('png','pdf'),#CairoPS
                      fig.width=3.5,fig.height=3,fig.path = params$figdir)

```

```{r libraries}
library('dplyr')
library('openxlsx')
library('fitdistrplus')
library('SHELF')
library('ggplot2')
library('sn')
library('knitr')
```

```{r}
source('functions_BPA.R')
breaks = c(-2,-1,0,1,2)
limits = c(-3,3)
limits2 = c(-3,10)

#theme_set(theme_bw(base_size = 12)) 

# Create a blank workbook - done in render file instead
# OUT <- createWorkbook()
```

# Retrive data 

```{r}
#Q1_ALI = c(66,66) ## need to do when testing the code without rendering
list_env_hocs <- pfunctions_hocs <- pfunctions_histo_hocs <- info_hocs <- env_hocs <- env_histo_hocs <- vector('list',length(hocs))
for (f in 1:length(hocs)){ 
  hoc <- hocs[f]

  source('PBA_health_outcome_category.R')
  pfunctions_hocs[[f]] <- pfunctions
  pfunctions_histo_hocs[[f]] <- pfunctions_histo 
  info_hocs[[f]] <- info
  env_hocs[[f]] <- df_env
  env_histo_hocs[[f]] <- df_env_histo
  list_env_hocs[[f]] <- list_env
}

clusters <- c(unique(info_hocs[[1]]$cluster),
              unique(info_hocs[[2]]$cluster),
              unique(info_hocs[[3]]$cluster),
              unique(info_hocs[[4]]$cluster),
              unique(info_hocs[[5]]$cluster))


```


```{r}
## create a modified version of get_p with the possibilty to select on expert of ALI at a time
get_p <- function(one_dose,loo='none',p_param=TRUE,expert = 'all'){

if(p_param){
p_i <- get_env(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_hocs[[1]],expert = expert)
p_m <- get_env(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_hocs[[2]])
p_n <- get_env(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_hocs[[3]])
p_r <- get_env(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_hocs[[4]])
p_c <- get_env(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_hocs[[5]])
}else{
p_i <- get_env(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[1]],expert = expert)
p_m <- get_env(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[2]])
p_n <- get_env(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[3]])
p_r <- get_env(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[4]])
p_c <- get_env(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[5]])
}

return(list(lower=1 - prod(1-p_c$lower_cdf)*
prod(1-p_i$lower_cdf)*
prod(1-p_m$lower_cdf)*
prod(1-p_n$lower_cdf)*
prod(1-p_r$lower_cdf),
upper = 1 - prod(1-p_c$upper_cdf)*
prod(1-p_i$upper_cdf)*
prod(1-p_m$upper_cdf)*
prod(1-p_n$upper_cdf)*
prod(1-p_r$upper_cdf)))
}
```


```{r}
# Derive the envelope of the probability of at least one 
## parametric 
dose = seq(-4,4,length.out = 400)

lowup_all <- lapply(1:length(dose),function(di){get_p(dose[di])})

df_env_all <- data.frame(lower_cdf=unlist(lapply(lowup_all,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all,function(x){x$upper})),dose = dose)

## histogram 
lowup_all_histo <- lapply(1:length(dose),function(di){get_p(dose[di],p_param = FALSE)})

df_env_all_histo <- data.frame(lower_cdf=unlist(lapply(lowup_all_histo,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all_histo,function(x){x$upper})),dose = dose)
```


```{r}
# Find 5th percentile by optimisation 

## parametric
objective1 <- function(d){(get_p(d)$lower-0.05)^2}

objective2 <- function(d){(get_p(d)$upper-0.05)^2}

df_opt <- data.frame(lower = optimize(objective2,interval = c(-10,10))$minimum,
                     upper = optimize(objective1,interval = c(-10,10))$minimum,
cdf = 0.05,mind = min(df_env_all$dose))

```



```{r}
# Derive envelope with and without allergic lung inflammation 
clid_remove = 1 #"Allergic lung inflammation "
lowup_all <- lapply(1:length(dose),function(di){get_p(dose[di],loo=clusters[clid_remove])})

df_env_all_noALI <- data.frame(lower_cdf=unlist(lapply(lowup_all,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all,function(x){x$upper})),dose = dose)

objective1 <- function(d){(get_p(d,loo=clusters[clid_remove])$lower-0.05)^2}

objective2 <- function(d){(get_p(d,loo=clusters[clid_remove])$upper-0.05)^2}

df_opt_noALI <- data.frame(lower = optimize(objective2,interval = c(-10,10))$minimum,
                     upper = optimize(objective1,interval = c(-10,10))$minimum,
cdf = 0.05,mind = min(df_env_all_noALI$dose))

df_opt1 <- data.frame(df_opt)
df_opt1$lower = df_opt$upper
df_opt1$upper = df_opt_noALI$lower

```


```{r}
# Calculate envelopes for different choices of percentiles

## parameteric 
perc = c(0.01,0.025,seq(0.05,0.95,by=0.05))
if(!usesavedoutputs){
df_calc_perc <- do.call('rbind',lapply(1:length(perc),function(ip){
objective1 <- function(d){(get_p(d)$lower-perc[ip])^2}

objective2 <- function(d){(get_p(d)$upper-perc[ip])^2}

df_opt <- data.frame(perc = perc[ip],
lower = optimize(objective2,interval = c(-10,10))$minimum,
upper = optimize(objective1,interval = c(-10,10))$minimum)
}))

save(df_calc_perc,file=paste0("env_",Q1_ALI[1],"_",Q1_ALI[2]))
}else{
load(file=paste0("env_",Q1_ALI[1],"_",Q1_ALI[2]))
}
# Add some sheets to the workbook
# addWorksheet(OUT,paste0("env_",Q1_ALI[1],"_",Q1_ALI[2]))
# Write the data to the sheets
#writeData(OUT, sheet = paste0("env_",Q1_ALI[1],"_",Q1_ALI[2]), x = df_calc_perc)


```


```{r}
## histogram 
if(!usesavedoutputs){
df_calc_perc_hist <- do.call('rbind',lapply(1:length(perc),function(ip){
objective1 <- function(d){(get_p(d,p_param=FALSE)$lower-perc[ip])^2}

objective2 <- function(d){(get_p(d,p_param=FALSE)$upper-perc[ip])^2}

df_opt <- data.frame(perc = perc[ip],
lower = optimize(objective2,interval = c(-10,10))$minimum,
upper = optimize(objective1,interval = c(-10,10))$minimum)
}))
save(df_calc_perc_hist,file=paste0("env_hist",Q1_ALI[1],"_",Q1_ALI[2]))
}else{
load(file=paste0("env_hist",Q1_ALI[1],"_",Q1_ALI[2]))
}

# Add some sheets to the workbook
#addWorksheet(OUT, paste0("envhisto_",Q1_ALI[1],"_",Q1_ALI[2]))
# Write the data to the sheets
#writeData(OUT, sheet = paste0("envhisto_",Q1_ALI[1],"_",Q1_ALI[2]), x = df_calc_perc)
```

# Sensitivity analysis envelope (repeated from combination since here we use different Q1 prob)

```{r}
## Leave one out - derive the 5th percentile for the envelope
clusters_all <- c('all',clusters)
if(!usesavedoutputs){
sa_c <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p(d,loo=clusters_all[clid])$lower-0.05)^2}

objective2 <- function(d){(get_p(d,loo=clusters_all[clid])$upper-0.05)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = 0.05,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))
save(sa_c,file=paste0("sa_c",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
  load(paste0("sa_c",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
```


```{r sa,fig.width = 6, fig.height=3}
ggplot(sa_c,aes(y=cluster,x=lower,fill=cluster))+
# geom_point() + 
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
 # xlim(-2,-1) + 
#  facet_wrap(~iter) +
  theme_bw()+
    ylab("cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name="5th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-2.5,2)) +
  ggtitle("Sensitivity analysis using leave-one-out")

```


```{r}
## Leave one out - derive the 5th percentile for the envelope
clid_remove = 1
clusters_all <- c('all',clusters[-clid_remove])

if(!usesavedoutputs){
sa_c_noALI <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p(d,loo=c(clusters[clid_remove],clusters_all[clid]))$lower-0.05)^2}

objective2 <- function(d){(get_p(d,loo=c(clusters[clid_remove],clusters_all[clid]))$upper-0.05)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = 0.05,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))
save(sa_c_noALI,file=paste0("sa_c_withoutALI",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
  load(paste0("sa_c_withoutALI",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
```


```{r sa_withoutALI,fig.width = 6, fig.height=3}
ggplot(sa_c_noALI,aes(y=cluster,x=lower,fill=cluster))+
# geom_point() + 
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
 # xlim(-2,-1) + 
#  facet_wrap(~iter) +
  theme_bw()+
    ylab("cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name="5th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-2.5,2)) +
  ggtitle("Sensitivity analysis using leave-one-out")

```

# SA against expert on ALI 

```{r}
## Calculate env per expert ALI
## takes a long time to run 
if(!usesavedoutputs){
df_per_expert <- lapply(1:14,function(expert){
## parametric
all <- lapply(1:length(dose),function(di){get_p(dose[di],expert = expert)})
## histogram 
all_histo <- lapply(1:length(dose),function(di){get_p(dose[di],p_param = FALSE,expert = expert)})

df_env_perexpert <- data.frame(dose = dose,
lower_cdf=unlist(lapply(all,function(x){x$lower})),
upper_cdf=unlist(lapply(all,function(x){x$upper})),
histo_lower_cdf=unlist(lapply(all_histo,function(x){x$lower})),
histo_upper_cdf=unlist(lapply(all_histo,function(x){x$upper})))
df_env_perexpert$expert = LETTERS[expert]
return(df_env_perexpert)
})
save(df_per_expert,file=paste0("df_per_expert",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
load(file=paste0("df_per_expert",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
```


```{r envQ1}
df_env_all$expert = 'all'
ggplot(data=do.call('rbind',df_per_expert),aes(x=dose,y=100*lower_cdf,fill = expert)) +
  geom_line(alpha=0.4)+
  geom_line(aes(x=dose,y=100*upper_cdf),colour = 'darkred',alpha = 0.4)+
  geom_line(data=df_env_all,aes(x=dose,y=100*upper_cdf),colour = 'blue') +
  geom_line(data=df_env_all,aes(x=dose,y=100*lower_cdf),colour = 'blue') +
  theme_bw()+
  ggtitle(paste(Q1_ALI[1],"-",Q1_ALI[2],"%")) +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", 
                     breaks=breaks, labels=10^breaks,limits = c(-2.5,3))

```

# POOL THE ESTIMATES WITHIN EACH CLUSTER

```{r}
# Derive the linear pool of the probability of at least one for all experts 
get_p_with_pool <- function(one_dose,loo='none',p_param=TRUE,linear_pool = TRUE,expert = 'all'){
if(linear_pool){
if(p_param){
p_i <- get_linear_pool(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_hocs[[1]],expert = expert)
p_m <- get_linear_pool(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_hocs[[2]])
p_n <- get_linear_pool(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_hocs[[3]])
p_r <- get_linear_pool(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_hocs[[4]])
p_c <- get_linear_pool(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_hocs[[5]])
}else{
p_i <- get_linear_pool(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[1]],expert = expert)
p_m <- get_linear_pool(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[2]])
p_n <- get_linear_pool(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[3]])
p_r <- get_linear_pool(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[4]])
p_c <- get_linear_pool(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[5]])
}
}else{
  if(p_param){ ##CHANGE CODE
p_c <- get_impagg(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_hocs[[1]])
p_i <- get_impagg(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_hocs[[2]])
p_m <- get_impagg(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_hocs[[3]])
p_n <- get_impagg(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_hocs[[4]])
p_r <- get_impagg(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_hocs[[5]])
}else{
p_c <- get_impagg(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[1]])
p_i <- get_impagg(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[2]])
p_m <- get_impagg(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[3]])
p_n <- get_impagg(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[4]])
p_r <- get_impagg(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[5]])
}
}
  if(linear_pool){
return(list(lower_pf=1 - prod(1-p_c$lower_cdf)*
prod(1-p_i$lower_cdf)*
prod(1-p_m$lower_cdf)*
prod(1-p_n$lower_cdf)*
prod(1-p_r$lower_cdf),
upper_pf=1 - prod(1-p_c$upper_cdf)*
prod(1-p_i$upper_cdf)*
prod(1-p_m$upper_cdf)*
prod(1-p_n$upper_cdf)*
prod(1-p_r$upper_cdf),
mid_pf=1 - prod(1-p_c$mid_cdf)*
prod(1-p_i$mid_cdf)*
prod(1-p_m$mid_cdf)*
prod(1-p_n$mid_cdf)*
prod(1-p_r$mid_cdf)))
  }else{
return(list(lower_pf=1 - prod(1-p_c$lower_cdf)*
prod(1-p_i$lower_cdf)*
prod(1-p_m$lower_cdf)*
prod(1-p_n$lower_cdf)*
prod(1-p_r$lower_cdf),
upper_pf=1 - prod(1-p_c$upper_cdf)*
prod(1-p_i$upper_cdf)*
prod(1-p_m$upper_cdf)*
prod(1-p_n$upper_cdf)*
prod(1-p_r$upper_cdf),
conf = (sum(p_c$conf)+sum(p_i$conf) + sum(p_m$conf) + sum(p_n$conf) + sum(p_r$conf))/(nrow(p_c)+nrow(p_i)+nrow(p_m)+nrow(p_n)+nrow(p_r))))
  }
}
```

```{r}
## parametric
linear_pool_all <- lapply(1:length(dose),function(di){get_p_with_pool(dose[di])})
## histogram 
linear_pool_all_histo <- lapply(1:length(dose),function(di){get_p_with_pool(dose[di],p_param = FALSE)})
```

```{r}
df_pool <- data.frame(dose = dose,
linear_pool_lower_cdf=unlist(lapply(linear_pool_all,function(x){x$lower_pf})),
linear_pool_upper_cdf=unlist(lapply(linear_pool_all,function(x){x$upper_pf})),
#linear_pool_mid_cdf=unlist(lapply(linear_pool_all,function(x){x$mid_pf})),
linear_pool_histo_lower_cdf=unlist(lapply(linear_pool_all_histo,function(x){x$lower_pf})),
linear_pool_histo_upper_cdf=unlist(lapply(linear_pool_all_histo,function(x){x$upper_pf})))#,
#linear_pool_histo_mid_cdf=unlist(lapply(linear_pool_all_histo,function(x){x$mid_pf})))
df_pool$expert = 'all'

```

```{r}
# Find 5th percentile by optimisation
get_perc_expert <- function(expert){
perc = c(0.01,0.025,seq(0.05,0.95,by=0.05))
df_calc_perc <- do.call('rbind',lapply(1:length(perc),function(ip){
objective1 <- function(d){(get_p_with_pool(d,expert = expert)$lower_pf-perc[ip])^2}

objective2 <- function(d){(get_p_with_pool(d,expert = expert)$upper_pf-perc[ip])^2}

#objective3 <- function(d){(get_p_with_pool(d,expert = expert)$mid_pf-perc[ip])^2}

#objective4 <- function(d){(df_pool$linear_pool_histo_lower_cdf[max(which(df_pool$dose<=d))]-perc[ip])^2}

#objective5 <- function(d){(df_pool$linear_pool_histo_upper_cdf[max(which(df_pool$dose<=d))]-perc[ip])^2}

#objective6 <- function(d){(df_pool$linear_pool_histo_mid_cdf[max(which(df_pool$dose<=d))]-perc[ip])^2}

df_opt <- data.frame(perc = perc[ip],
lower = optimize(objective2,interval = c(-10,10))$minimum,
upper = optimize(objective1,interval = c(-10,10))$minimum)#,
#mid = optimize(objective3,interval = c(-10,10))$minimum)#,
#lower_histo = optimize(objective5,interval = c(min(df_pool$dose),max(df_pool$dose)))$minimum,
#upper_histo = optimize(objective4,interval = c(min(df_pool$dose),max(df_pool$dose)))$minimum,
#mid_histo = optimize(objective6,interval = c(min(df_pool$dose),max(df_pool$dose)))$minimum)
}))

if(expert == 'all'){
df_calc_perc$expert = 'all'
}else{
df_calc_perc$expert = LETTERS[expert]
  
}
return(df_calc_perc)
}

df_calc_perc <- get_perc_expert(expert='all')
```


```{r}
## calculate linear pool for each expert in ALI
if(!usesavedoutputs){
df_pool_expert <- lapply(1:14,function(expert){
## parametric
linear_pool_all <- lapply(1:length(dose),function(di){get_p_with_pool(dose[di],expert = expert)})
## histogram 
linear_pool_all_histo <- lapply(1:length(dose),function(di){get_p_with_pool(dose[di],p_param = FALSE,expert = expert)})

df_pool <- data.frame(dose = dose,
linear_pool_lower_cdf=unlist(lapply(linear_pool_all,function(x){x$lower_pf})),
linear_pool_upper_cdf=unlist(lapply(linear_pool_all,function(x){x$upper_pf})),
#linear_pool_mid_cdf=unlist(lapply(linear_pool_all,function(x){x$mid_pf})),
linear_pool_histo_lower_cdf=unlist(lapply(linear_pool_all_histo,function(x){x$lower_pf})),
linear_pool_histo_upper_cdf=unlist(lapply(linear_pool_all_histo,function(x){x$upper_pf})))#,
#linear_pool_histo_mid_cdf=unlist(lapply(linear_pool_all_histo,function(x){x$mid_pf})))
df_pool$expert = LETTERS[expert]
return(df_pool)
})

## percentiles
df_calc_perc_expert <- lapply(1:14,function(expert){
df_calc_perc <- get_perc_expert(expert=expert)
return(df_calc_perc)
})
save(df_pool_expert,df_calc_perc_expert,file=paste0("df_calc_perc_expert",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
  load(paste0("df_calc_perc_expert",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
df_calc_multi <- rbind(df_calc_perc,do.call('rbind',df_calc_perc_expert))
# Add some sheets to the workbook
# addWorksheet(OUT,paste0("linpool_",Q1_ALI[1],"_",Q1_ALI[2]))
# Write the data to the sheets
#writeData(OUT, sheet = paste0("linpool_",Q1_ALI[1],"_",Q1_ALI[2]), x = df_calc_multi[,c("perc","lower","upper")])

df_cm <- df_calc_multi[,c("perc","expert","lower","upper")]
save(df_cm,file=paste0("linpool_",Q1_ALI[1],"_",Q1_ALI[2]))

df_pool_multi <- rbind(df_pool,do.call('rbind',df_pool_expert))
df_pool_all <- df_pool[,c("dose","linear_pool_lower_cdf","linear_pool_upper_cdf")]
df_pool_all_histo <- df_pool[,c("dose","linear_pool_histo_lower_cdf","linear_pool_histo_upper_cdf")]
```

##  Probability that the estimated lowest BMD is less than 0.93 

```{r}
get_p_with_pool(one_dose=log10(0.93),loo='none',p_param=TRUE,linear_pool = TRUE,expert = 'all')

get_p_with_pool(one_dose=log10(0.93),loo='none',p_param=FALSE,linear_pool = TRUE,expert = 'all')
```


```{r env_linearpool}
ggplot(data=do.call('rbind',df_pool_expert)) +
#  geom_ribbon(aes(x=dose,ymin=linear_pool_lower_cdf,ymax=linear_pool_upper_cdf,fill=expert,color=expert),alpha = 0.1) + 
geom_line(data=df_env_all,aes(x=dose,y=100*lower_cdf),col="black")+
geom_line(data=df_env_all,aes(x=dose,y=100*upper_cdf),col="black")+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_lower_cdf),col="red",linetype='dashed')+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_upper_cdf),col="red",linetype='dashed')+
  theme_bw()+
  #scale_fill_brewer(type="qual")+
  ggtitle(paste(Q1_ALI[1],"-",Q1_ALI[2],"%")) + 
#  ggtitle("Uncertainty in lowest BMD across clusters",subtitle = "envelope considering differences between experts (black), \n and linear pool (red)") +
  ylab("Cumulative probability (%)") +
scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-2.5,3))


```


# GRAPH COMPARING LINEAR POOL OF PARAMETRIC AND HISTOGRAM


```{r paramhisto_15}
# derive linear pool for histogram

# compare parametric and histogram 
 colnames(df_pool_all_histo) <-  colnames(df_pool_all)
 df_pool_all$distribution = 'parametric'
 df_pool_all_histo$distribution = 'histogram'
df_ph <- rbind(df_pool_all,df_pool_all_histo)

ggplot(data=df_ph,aes(x=dose,y=100*linear_pool_lower_cdf,col = distribution)) +
  scale_color_manual(values = c('black','darkred'))+
  geom_line()+
  geom_line(aes(x=dose,y=100*linear_pool_upper_cdf)) + 
  geom_hline(yintercept = 0.15*100,col='blue') +
#  geom_segment(data=df_opt,aes(x=mind,xend=upper,y=100*cdf,yend=100*cdf),col='blue')+
theme_bw()+
  theme(legend.position = "none")+
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = NULL)

```

# Sensitivity analysis LEAVE ONE OUT 5 and 15th percentile 

```{r sa_linearpool_5th, fig.width = 6, fig.height = 3}
clusters_all <- c('all',clusters)
q = 0.05
## Evaluate influence on the 5th and 15th percentile of lowest BMD of clusters using leave-one-out
  if(!usesavedoutputs){
sa_c_linear_pool <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p_with_pool(d,loo=clusters_all[clid])$lower-q)^2}

objective2 <- function(d){(get_p_with_pool(d,loo=clusters_all[clid])$upper-q)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = q,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))
save(sa_c_linear_pool,file=paste0("sa_c_linear_pool_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
  }else{
load(file=paste0("sa_c_linear_pool_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
  }
  
ggplot(sa_c_linear_pool,aes(y=cluster,x=lower,fill=cluster))+
# geom_point() + 
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
 # xlim(-2,-1) + 
#  facet_wrap(~iter) +
  theme_bw()+
    ylab("Cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name=paste0(100*q,"th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)"), breaks=breaks, labels=10^breaks,limits = c(-2,1)) 

```


```{r sa_linearpool_15th, fig.width = 6, fig.height = 3}
clusters_all <- c('all',clusters)
q = 0.15
## Evaluate influence on the 5th and 15th percentile of lowest BMD of clusters using leave-one-out
  if(!usesavedoutputs){
sa_c_linear_pool <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p_with_pool(d,loo=clusters_all[clid])$lower-q)^2}

objective2 <- function(d){(get_p_with_pool(d,loo=clusters_all[clid])$upper-q)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = q,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))
save(sa_c_linear_pool,file=paste0("sa_c_linear_pool_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
  }else{
load(file=paste0("sa_c_linear_pool_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
  }
  
ggplot(sa_c_linear_pool,aes(y=cluster,x=lower,fill=cluster))+
# geom_point() + 
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
 # xlim(-2,-1) + 
#  facet_wrap(~iter) +
  theme_bw()+
    ylab("Cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name=paste0(100*q,"th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)"), breaks=breaks, labels=10^breaks,limits = c(-2,1)) 

```

```{r sa_linearpool_5th_withoutALI, fig.width = 6, fig.height = 3}
## Without ALI
clusters_all <- c('all',clusters[-clid_remove])
q <- 0.05
## Evaluate influence on the 5th and 15th percentile of lowest BMD of clusters using leave-one-out
if(!usesavedoutputs){
sa_c_linear_pool <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p_with_pool(d,loo=c(clusters_all[clid],clusters[clid_remove]))$lower-q)^2}

objective2 <- function(d){(get_p_with_pool(d,loo=c(clusters_all[clid],clusters[clid_remove]))$upper-q)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = q,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))

save(sa_c_linear_pool,file=paste0("sa_c_linear_pool_withoutALI_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
load(file=paste0("sa_c_linear_pool_withoutALI_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
  
ggplot(sa_c_linear_pool,aes(y=cluster,x=lower,fill=cluster))+
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
  theme_bw()+
    ylab("Cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name=paste0(100*q,"th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)"), breaks=breaks, labels=10^breaks,limits = c(-2,1)) 

```

```{r sa_linearpool_15th_withoutALI, fig.width = 6, fig.height = 3}
## Without ALI
clusters_all <- c('all',clusters[-clid_remove])
q <- 0.15
## Evaluate influence on the 5th and 15th percentile of lowest BMD of clusters using leave-one-out
if(!usesavedoutputs){
sa_c_linear_pool <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p_with_pool(d,loo=c(clusters_all[clid],clusters[clid_remove]))$lower-q)^2}

objective2 <- function(d){(get_p_with_pool(d,loo=c(clusters_all[clid],clusters[clid_remove]))$upper-q)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = q,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))

save(sa_c_linear_pool,file=paste0("sa_c_linear_pool_withoutALI_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
load(file=paste0("sa_c_linear_pool_withoutALI_",q,"_",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
  
ggplot(sa_c_linear_pool,aes(y=cluster,x=lower,fill=cluster))+
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
  theme_bw()+
    ylab("Cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name=paste0(100*q,"th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)"), breaks=breaks, labels=10^breaks,limits = c(-2,1)) 


```

# Different experts on ALI 

```{r}
## show all experts without different colours
if(FALSE){
  ggplot(data=do.call('rbind',df_pool_expert),aes(x=dose,y=linear_pool_lower_cdf,fill = expert)) +
  geom_line(alpha=0.4)+
  geom_line(aes(x=dose,y=linear_pool_upper_cdf),colour = 'darkred',alpha = 0.4)+
  #geom_line(data=env_exp_ALI[[1]],aes(x=dose+3,y=upper_cdf),colour = 'blue') +
  #geom_line(data=env_exp_ALI[[1]],aes(x=dose+3,y=lower_cdf),colour = 'blue') +
  theme_bw()+
 # facet_wrap(~Q2) + 
  ggtitle("Uncertainty in lowest BMD across clusters",
          subtitle = paste("linear pools for one expert on ALI at a time")) +
  ylab("cumulative probability") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", 
                     breaks=breaks, labels=10^(breaks),limits = NULL)
}
```


# Sensitivity analysis - consider possible dependencies between clusters 


```{r}

if(SADEP){
get_p_with_dependencies <- function(one_dose,loo='none',dep,rho){

p_c <- get_linear_pool(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_hocs[[1]])
p_i <- get_linear_pool(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_hocs[[2]])
p_m <- get_linear_pool(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_hocs[[3]])
p_n <- get_linear_pool(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_hocs[[4]])
p_r <- get_linear_pool(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_hocs[[5]])

# turn probabilities to 1 or zero where there are dependencies 
rbind(p_c[p_c$cluster %in% dep,1:2],
p_i[p_i$cluster %in% dep,1:2],
p_m[p_m$cluster %in% dep,1:2],
p_n[p_n$cluster %in% dep,1:2],
p_r[p_r$cluster %in% dep,1:2])

p_c[p_c$cluster %in% dep,1:2] = 0
p_i[p_i$cluster %in% dep,1:2] = 0
p_m[p_m$cluster %in% dep,1:2] = 0
p_n[p_n$cluster %in% dep,1:2] = 0
p_r[p_r$cluster %in% dep,1:2] = 0


# derive joint probability for dependent clusters 
i=as.numeric(cut(which(dep[1]==clusters),c(0,4,9,15,18,21)))
clid_i=which(unlist(lapply(list_env_hocs[[i]],function(ee){ee$cluster[1]})) %in% dep[1])
j=as.numeric(cut(which(dep[2]==clusters),c(0,4,9,15,18,21)))
clid_j=which(unlist(lapply(list_env_hocs[[j]],function(ee){ee$cluster[1]})) %in% dep[2])

ddd <-  list_env_hocs[[i]][[clid_i]]$dose
pfunction_1 <- do.call('rbind',lapply(1:length(ddd),function(di){get_linear_pool(info_hocs[[i]][(info_hocs[[i]]$cluster %in% dep[1]),],ddd[di],pfunctions_hocs[[i]])}))

ddd <-  list_env_hocs[[j]][[clid_j]]$dose
pfunction_2 <- do.call('rbind',lapply(1:length(ddd),function(di){get_linear_pool(info_hocs[[j]][(info_hocs[[j]]$cluster %in% dep[2]),],ddd[di],pfunctions_hocs[[j]])}))

jointprob = approx_jointprobability_linear_pool(target_d=one_dose,rho=rho,pfunction_1=pfunction_1,pfunction_2=pfunction_2,niter=15000)$probisd

return(list(lower=1 - prod(1-p_c$lower_cdf)*
prod(1-p_i$lower_cdf)*
prod(1-p_m$lower_cdf)*
prod(1-p_n$lower_cdf)*
prod(1-p_r$lower_cdf)*
  (max(jointprob)),
upper = 1 - prod(1-p_c$upper_cdf)*
prod(1-p_i$upper_cdf)*
prod(1-p_m$upper_cdf)*
prod(1-p_n$upper_cdf)*
prod(1-p_r$upper_cdf)*
  (min(jointprob))))
}
}
```

## Derive the envelope of the probability of at least one considering dependency between Allergic Lung Inflammation and Male and Female Reprotoxicity respectively

```{r}
if(SADEP){
temp <- range(df_pool_all$dose[df_pool_all$linear_pool_upper_cdf>0.01 & df_pool_all$linear_pool_lower_cdf<0.99])
dose_2 <- seq(temp[1],temp[2],length.out = 100)
get_dep <- function(clid_deps,rhos){
do.call('rbind',lapply(1:length(rhos),function(rid){
lowup_all_dep <- lapply(1:length(dose_2),function(di){get_p_with_dependencies(one_dose=dose_2[di],loo='none',dep =clusters[clid_deps],rho=rhos[rid])})

data.frame(lower_cdf=unlist(lapply(lowup_all_dep,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all_dep,function(x){x$upper})),dose = dose_2,rho = rhos[rid])
}
))
}
}
```

Male 

```{r dep_ALI_male_linearpool}
if(SADEP){
if(!usesavedoutputs){
df_dep <- get_dep(clid_deps=c(1,16),rhos = c(-0.9,0,0.5,0.9))
df_dep$correlation = as.character(df_dep$rho)

save(df_dep,file=paste0("df_dep_male",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
  load(paste0("df_dep_male",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
ggplot(data=df_dep,aes(x=dose,y=100*lower_cdf,color = correlation)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf,color = correlation))+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_lower_cdf),col="black",alpha=0.7)+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_upper_cdf),col="black",alpha=0.7)+
theme_bw()+
  theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7)) +
 theme(plot.title = element_text(size = 8)) +
  ggtitle("Dependence between Allergic Lung Inflammation \n and Male reprotoxicity") +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)

}

```

```{r dep_ALI_female_linearpool}

if(SADEP){
if(!usesavedoutputs){
   df_dep <- get_dep(clid_deps=c(1,17),rhos = c(-0.9,0,0.5,0.9))
df_dep$correlation = as.character(df_dep$rho)
save(df_dep,file=paste0("df_dep_female",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
  load(paste0("df_dep_female",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}

ggplot(data=df_dep,aes(x=dose,y=100*lower_cdf,color = correlation)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf,color = correlation))+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_lower_cdf),col="black",alpha=0.7)+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_upper_cdf),col="black",alpha=0.7)+
theme_bw()+
 theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7)) +
    theme(plot.title = element_text(size = 8)) +
  ggtitle("Dependence between Allergic Lung Inflammation \n and Female reprotoxicity") +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)

}

```

```{r dep_male_female_linearpool}

if(SADEP){
if(!usesavedoutputs){
df_dep <- get_dep(clid_deps=c(16,17),rhos = c(-0.9,0,0.5,0.9))
df_dep$correlation = as.character(df_dep$rho)

save(df_dep,file=paste0("df_dep_malefemale",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}else{
  load(paste0("df_dep_malefemale",Q1_ALI[1],"_",Q1_ALI[2],".Rdata"))
}
ggplot(data=df_dep,aes(x=dose,y=100*lower_cdf,color = correlation)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf,color = correlation))+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_lower_cdf),col="black",alpha=0.7)+
geom_line(data=df_pool_all,aes(x=dose,y=100*linear_pool_upper_cdf),col="black",alpha=0.7)+
theme_bw()+
  theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7)) +
   theme(plot.title = element_text(size = 8)) +
  ggtitle("Dependence between Male and \n Female reprotoxicity") +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)


}

```


```{r}
if(FALSE){
## show overlap of expert ALI results
ggplot(data=do.call('rbind',df_pool_expert)) +
  geom_ribbon(aes(x=dose,ymin=linear_pool_lower_cdf,ymax=linear_pool_upper_cdf,fill=expert,color=expert),alpha = 0.1) + 
geom_line(data=df_env_all,aes(x=dose,y=lower_cdf),col="black",size = 1)+
geom_line(data=df_env_all,aes(x=dose,y=upper_cdf),col="black",size = 1)+
geom_line(data=df_pool_all,aes(x=dose,y=linear_pool_lower_cdf),col="red",linetype='dashed',size=1)+
geom_line(data=df_pool_all,aes(x=dose,y=linear_pool_upper_cdf),col="red",linetype='dashed',size=1)+
  theme_bw()+
  #scale_fill_brewer(type="qual")+
  ggtitle("Uncertainty in lowest BMD across clusters",subtitle = "black: envelope considering differences between experts, \n red: linear pool, coloured: linear pool per expert for ALI") +
  ylab("cumulative probability") +
scale_x_continuous(name="Lowest BMD across all clusters (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-2.5,3))# +
  #ylim(c(0,0.3))
ggsave(paste("perALIover_",Q1_ALI[1],"_",Q1_ALI[2],".png"),width = 7, height = 6)
}
```

```{r}
#show linear pool for different experts ALI
if(FALSE){
ggplot(data=do.call('rbind',df_pool_expert)) +
  geom_ribbon(aes(x=dose,ymin=linear_pool_lower_cdf,ymax=linear_pool_upper_cdf,fill=expert,color=expert),alpha = 0.5) + 
geom_line(data=df_env_all[,colnames(df_env_all)!="expert"],aes(x=dose,y=lower_cdf),col="black",size = 1)+
geom_line(data=df_env_all[,colnames(df_env_all)!="expert"],aes(x=dose,y=upper_cdf),col="black",size = 1)+
geom_line(data=df_pool_all,aes(x=dose,y=linear_pool_lower_cdf),col="red",linetype='dashed',size=1)+
geom_line(data=df_pool_all,aes(x=dose,y=linear_pool_upper_cdf),col="red",linetype='dashed',size=1)+
  theme_bw()+
  facet_wrap(~expert) +
 #scale_fill_brewer(type="qual")+
  ggtitle("Uncertainty in lowest BMD across clusters",subtitle = "black: envelope considering differences between experts, \n red: linear pool, coloured: linear pool per expert for ALI") +
  ylab("cumulative probability") +
scale_x_continuous(name="Lowest BMD across all clusters (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-2.5,3))# +
  #ylim(c(0,0.3))
ggsave(paste("perALIfacet_",Q1_ALI[1],"_",Q1_ALI[2],".png"),width = 10, height = 10)
}
```

```{r}
## plot intervals for 5th percentile with overlay linear pool
if(FALSE){
dfp <- df_calc_multi[df_calc_multi$perc == 0.05 & df_calc_multi$expert!="all",]
dfpall <- df_calc_multi[df_calc_multi$perc == 0.05 & df_calc_multi$expert=="all",]
dfp$expert = factor(dfp$expert,levels = c(LETTERS[1:14]))
dfp$expert = factor(dfp$expert,levels=rev(levels(dfp$expert)))
ggplot(dfp,aes(y=expert,x=lower,fill=expert))+
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=expert))+
  geom_vline(xintercept=dfpall$lower,col='red',alpha = 0.5) +
  geom_vline(xintercept=dfpall$upper,col='red',alpha = 0.5) +
  theme_bw()+
  ylab("expert") +
  theme(legend.position = "none") +
  scale_x_continuous(name="Lowest BMD across all clusters  (HED, ng BPA/kg bw per day)", breaks=c(-2,-1,0,1), labels=10^c(-2,-1,0,1),limits = c(-2,1)) +
  ggtitle("Linear pool of 5th percentile", subtitle="all experts (red)")
ggsave(paste("5perclinearpool_v2_",Q1_ALI[1],"_",Q1_ALI[2],".png"),width = 7, height = 6)
}
```


```{r}
#plot density curves of the experts per ALI
if(FALSE){
df_sel <-  do.call('rbind',lapply(1:14,function(jj){
    
    dat <- df_per_expert[[jj]]
    x = dat$dose
    cdf = dat$lower_cdf
    sam_lower = approx(cdf,x,runif(2*10^4),rule=2,ties=mean)$y
    cdf = dat$upper_cdf
    sam_upper = approx(cdf,x,runif(2*10^4),rule=2,ties=mean)$y
    data.frame(xl=sam_lower,xu=sam_upper,expert = LETTERS[jj])
  }))

ggplot(df_sel, aes(x = xl, group = expert)) + 
  geom_density(colour = "black",alpha = 0.4) +
  geom_density(aes(x = xu),colour = 'darkred',alpha = 0.4) +
  theme_bw()+
  ggtitle("Uncertainty in lowest BMD across clusters",
          subtitle = "Densities per expert for ALI") +
  ylab("probability density") +
  scale_x_continuous(name="Lowest BMD across all clusters (HED, ng BPA/kg bw per day)", 
                     breaks=breaks, labels=10^(breaks),limits = NULL)
ggsave(paste0("density_graphs_",Q1_ALI[1],"_",Q1_ALI[2],".png"),width = 7, height = 6)
}
```

