---
title: "Probability function for clusters and experts in a health outcome category"
author: "Ullrika Sahlin"
date: "`r Sys.Date()`"
params: 
  hocs: c('immunotox','metabolic','neurotox','repro','carcino')
  probmassoutside: 0.001
  origALI: FALSE
  hoc: 'immunotox'
  fit_distributions: FALSE
  Q1_ALI: c(66,66)
  figdir: figures
output:
  html_document:
    df_print: paged
    self_contained: true
---

```{r setup, include=FALSE}
hocs <- params$hocs
probmassoutside <- params$probmassoutside
origALI <- params$origALI
hoc <- params$hoc
fit_distributions <- params$fit_distributions
Q1_ALI = params$Q1_ALI

knitr::opts_chunk$set(dev = c('png','pdf'),
                      fig.width=6,fig.height=4,fig.path = params$figdir)
```

```{r libraries, include = FALSE}
library('dplyr')
library('openxlsx')
library('fitdistrplus')
library('SHELF') # modified version
library('ggplot2')
library('sn')

#theme_set(theme_bw(base_size = 12)) 

source('functions_BPA.R')
```

# Select data file   
```{r}
if(hoc == 'carcino'){
expert_xlsx = c(paste0("clusterdata/","BPA uncertainty analysis CARCINO - expert A.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis CARCINO - expert B_ullrika.xlsm"))
}

if(hoc == 'immunotox'){
  if(origALI){
expert_xlsx = c(paste0("clusterdata/","BPA uncertainty analysis IMMUNOTOX expert A v2.xlsm"),
expert_xlsx = paste0("clusterdata/","BPA uncertainty analysis IMMUNOTOX expert B v2.xlsm"))
     }else{
expert_xlsx = c(paste0("clusterdata/","BPA uncertainty analysis IMMUNOTOX expert A v3_noALI.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis IMMUNOTOX expert B v3_noALI.xlsm"))
expertJuly12th_xlsx = paste0("clusterdata/","CREATE roulette CSV file v2 - WITH REVISED JUDGEMENTS FROM EXPERT N.xlsx")
}
}

if(hoc == 'metabolic'){
expert_xlsx = c(paste0("clusterdata/","BPA uncertainty analysis METABOLIC - expert A.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis METABOLIC - expert B.xlsm"))
}

if(hoc == 'neurotox'){
expert_xlsx = c(paste0("clusterdata/","BPA uncertainty analysis NEUROTOX - expert A.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis NEUROTOX - expert B.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis NEUROTOX - expert C.xlsm"))
}

if(hoc == 'repro'){
expert_xlsx = c(paste0("clusterdata/","BPA uncertainty analysis REPRO - expert A.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis REPRO - expert B v2.xlsm"),
paste0("clusterdata/","BPA uncertainty analysis REPRO - expert C v2.xlsm"))
}

sheet = "Summary data"

```

# Extract data and fit distribution to Q2 

All doses are transformed into nano unit when extracting elicited data

```{r fit}
if(fit_distributions){
df_group <- lapply(1:length(expert_xlsx),function(expert){
  ## Cluster
cluster_nams <- read.xlsx(xlsxFile=expert_xlsx[expert],sheet= sheet, rows = 2, cols = 2:10,colNames = FALSE)
cluster_ids <- grep("START HERE",cluster_nams,invert=TRUE)
cluster_nams <- as.character(cluster_nams[grep("START HERE",cluster_nams,invert=TRUE)])
if(length(cluster_nams)>0){
df_cluster <- lapply(1:length(cluster_nams),function(clid){
  ## Q1 and Q2
df <- do.one.data.extration(expert,cluster_ids[clid])## transformation to nano scale
df$cluster = cluster_nams[clid]
df$fit <- do.one.fit(df,fit.mixture = TRUE)  
return(df)
})
names(df_cluster) <- cluster_nams

}else{df_cluster <- NA}
return(df_cluster)
})
if(hoc != "immunotox" | origALI){
save(df_group,file=paste('fit_',hoc,probmassoutside,'.Rdata'))
}

if(hoc == "immunotox" & !origALI){ # add the judgements from July 12
df_noALI <-  df_group
df_ALI <- lapply(1:14,function(expert){
  df <- do.one.data.extration_12july(expert,Q1 = Q1_ALI/100)
df$cluster = "Allergic lung inflammation "
df$fit <- do.one.fit(df,fit.mixture = TRUE)
df_cluster <- vector('list',1)
df_cluster[[1]] <- df
names(df_cluster) <- "Allergic lung inflammation "
return(df_cluster)
})

df_group <- append(df_ALI,df_noALI)
  save(df_group,file=paste('fit_revised',hoc,probmassoutside,'.Rdata'))
  }
}else{
  if(hoc == "immunotox" & !origALI){
load(file=paste('fit_revised',hoc,probmassoutside,'.Rdata'))
  }else{
load(file=paste('fit_',hoc,probmassoutside,'.Rdata'))
}}
```

# Combine the answers to Q1 and Q2 into a probability function per cluster and expert

Probability functions derived from Q1 and Q2 using parametric distributions or interpolation from the roulette histograms.

```{r}
# data frame for elicited data
df.pq <- make_distr_dataframe(df_group) 

pfunctions <- get_pfunctions(df_group) 
pfunctions_histo <- get_pfunctions_histo(df_group)

# info about the structure in the pfunctions 
info <- do.call('rbind',lapply(1:length(pfunctions),function(i){
  do.call('rbind',lapply(1:length(pfunctions[[i]]),function(j){data.frame(i=i,j=j,expert = pfunctions[[i]][[j]]$expert, cluster = pfunctions[[i]][[j]]$cluster)}))
  }))
```


```{r clusters_experts, fig.width=6, fig.height = 5}
# Plot lower and upper cdf for each cluster and expert
plot_clusters(df.pq)
```


```{r clusters_oneexpert, fig.width = 6, fig.height = 3}
# Plot lower and upper cdf for one cluster and one expert
if(hoc == "immunotox"){
plot_clusters_oneexpert(df.pq,experttoplot = 2)
}
```

# Aggregate over experts into an envelope considering differences between experts  

```{r}
dose_curve = seq(-4,4,length.out = 300)

df_env <- get_env(info,dose_curve,pfunctions)
df_env$type = 'parametric'

df_env_histo <- get_env(info,dose_curve,pfunctions_histo)
df_env_histo$type = 'histogram'

list_env <- get_env_list(info,dose_curve,pfunctions)  # the list version is used in some functions
```


```{r}
# Plot parametric distributions comparing experts 
eids = unique(info$expert)
unc_expert <- lapply(1:length(eids),function(eid){
  temp <- get_env(info[info$expert==eids[eid],],dose_curve,pfunctions)
  temp$expert = eids[eid]
  return(temp)
})
df.pq_range <- do.call('rbind',unc_expert)
df.pq_range$type = 'parametric'

plot_experts(df.pq_range)

```


```{r}
## Plot interpolation between histograms comparing experts 
if(FALSE){
unc_expert_histo <- lapply(1:length(eids),function(eid){
  temp <- get_env(info[info$expert==eids[eid],],dose_curve,pfunctions_histo)
  temp$expert = eids[eid]
  return(temp)
})

df.pq_range_histo <- do.call('rbind',unc_expert_histo)
df.pq_range_histo$type = 'histogram' 

plot_experts(df.pq_range_histo)
}
```



```{r}
## Plot envelope comparing parametric and histogram 
if(FALSE){
ggplot(data=rbind(df_env,df_env_histo),aes(x=dose,y=100*lower_cdf,linetype=type)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf))+
theme_bw()+
  scale_x_continuous(name="Lowest BMD in the cluster (HED, ng BPA/kg bw per day)", breaks=c(-4,-2,0,2), labels=10^c(-4,-2,0,2),limits = c(-4,4)) + 
  #ggtitle("Envelope of uncertainty distributions") +
  ylab("cumulative probability") +
  ylim(0,100) +
  facet_wrap(~cluster,scale = "free")
}
```


```{r}
# Plot parametric distributions and corresponding envelope in the same graph for each cluster 
if(FALSE){
  plot_experts_with_env(df.pq_range,df_env)
} 
```

```{r, onecluster_oneexpert_env, fig.width = 5, fig.height = 3}
if(hoc == "immunotox"){
#cls <- unique(df_env$cluster)
#for(clid in 1:length(cls)){
clid = 1
plot_experts_with_env_onecluster(df.pq_range,df_env,clid=clid)
#}
}
```


```{r}
# Plot histograms and corresponding envelope in the same graph for each cluster 
#plot_experts_with_env(df.pq_range_histo,df_env_histo)
```


```{r}
# Plot envelope and linear pool of upper and lower bounds 

#plot_experts_with_env_linear_pool(df.pq_range_histo,df_env_histo)
```

```{r ALI_judgements, fig.width = 6, fig.height = 4}
if(hoc == "immunotox" & !origALI){
df_ALI <- do.call('rbind',lapply(1:length(df_group),function(expert){
  df_group[[expert]]$`Allergic lung inflammation `$fit$df_fit 
 }))

df_ALI$expertnr = df_ALI$expert
df_ALI$expert = LETTERS[df_ALI$expertnr]
xa_ALI = c(-2,0,2,4)  

ggplot(df_ALI,aes(x=log10dd,y=pdf,col=expert)) + 
  geom_line() + 
    ylab('Probability density') +
    ggtitle('Allergic lung inflammation') +
    scale_x_continuous(name="Estimated lowest BMD in this cluster \n (HED, ng BPA/kg bw per day)", breaks=xa_ALI, labels=10^xa_ALI) +
  theme(legend.position = "none")
}
```
