---
title: "BPA calculation of BMD and overall uncertainty"
author: "Ullrika Sahlin"
date: "`r Sys.Date()`"
params: 
  hocs: c('immunotox','metabolic','neurotox','repro','carcino')
  probmassoutside: 0.001
  origALI: FALSE
  fit_distributions: FALSE
  Q1_ALI: c(66,66)
  figdir: figures_comb
output:
  html_document:
    df_print: paged
    self_contained: true
---

```{r setup2, include=FALSE}
hocs <- params$hocs
probmassoutside <- params$probmassoutside
origALI <- params$origALI
fit_distributions <- params$fit_distributions
Q1_ALI = params$Q1_ALI
## when testing this RMD use the following
#Q1_ALI = c(50,90)
#origALI = TRUE
#hocs = c('immunotox','metabolic','neurotox','repro','carcino')

knitr::opts_chunk$set(dev = c('png','pdf'),
                      fig.width=3.5,fig.height=3,fig.path = params$figdir)
```

```{r libraries, include = FALSE}
library('dplyr')
library('openxlsx')
library('ggplot2')
library('sn')
library('knitr')
```

```{r}
source('functions_BPA.R')
breaks = c(-2,-1,0,1,2)
limits = c(-3,3)
limits2 = c(-3,10)

#theme_set(theme_bw(base_size = 12)) 
```

# Run first fitting and creation of functions for each health outcome category

```{r}
list_df_Q2 <- list_df_Q1 <- list_env_hocs <- pfunctions_hocs <- pfunctions_histo_hocs <- info_hocs <- env_hocs <- env_histo_hocs <- vector('list',length(hocs))
for (f in 1:length(hocs)){ 
  hoc <- hocs[f]
  
  source('PBA_health_outcome_category.R')
  pfunctions_hocs[[f]] <- pfunctions
  pfunctions_histo_hocs[[f]] <- pfunctions_histo 
  info_hocs[[f]] <- info
  env_hocs[[f]] <- df_env
  env_histo_hocs[[f]] <- df_env_histo
  list_env_hocs[[f]] <- list_env
  list_df_Q1[[f]] <- df_Q1
 list_df_Q2[[f]] <- df_Q2
   
}
```

# Merge info from all clusters 

```{r}
clusters <- c(unique(info_hocs[[1]]$cluster),
              unique(info_hocs[[2]]$cluster),
              unique(info_hocs[[3]]$cluster),
              unique(info_hocs[[4]]$cluster),
              unique(info_hocs[[5]]$cluster))
```


## Plot Q1
```{r probQ1, fig.width = 6, fig.height= 10}
if(origALI){
  
#The 'standard' order the WG is using is as follows: immunotoxicity, metabolic effects, neurotoxicity and developmental neurotoxicity, reproductive and developmental toxicity, and carcinogenicity and mammary gland proliferative effects. 

dfq_org <- do.call('rbind',list_df_Q1)
  dfq_org$expertnr = dfq_org$expert
  dfq_org$expert = LETTERS[dfq_org$expertnr]
dfq_org$cluexp <- paste(dfq_org$cluster,dfq_org$expert)
write.xlsx(dfq_org,file='Q1probs.xlsx')

dfq_org$cluexp <- factor(dfq_org$cluexp,levels = dfq_org$cluexp[length(dfq_org$cluexp):1])
levels(dfq_org$cluexp)
lev1 <- levels(dfq_org$cluexp)
ord <- c(4,8,3,7,2,6,1,5, 
         11,15,10,13,9,12,14,
         17,22,16,19,21,18,20,
         28,34,27,33,26,32,25,31,24,30,23,29,
         39,44,38,43,37,42,36,41,35,40) 
lev2 <- lev1[ord]
dfq_org$cluexp <- factor(dfq_org$cluexp,levels = lev2)
dfqlower <- dfq_org
dfqlower$value <- dfq_org$lower
dfqlower$bound <- "b"
dfqupper <- dfq_org
dfqupper$value <- dfq_org$upper-dfq_org$lower
dfqupper$bound <- "a"
dfq <- rbind(dfqlower[,-c(5,6)],dfqupper[,-c(5,6)])
hline <- c(8.5,15.5,22.5,34.5)
#hline <- hline[2:4]
#dfq$nr <- nrow(dfq):1
dfq %>% 
ggplot(aes(y = cluexp, x = value*100, fill=bound)) +
geom_bar(position="stack",stat="identity",width = 0.5) +
theme_bw() +
scale_fill_manual(values=c("gray","NA")) +
  geom_hline(yintercept = hline,col='black')+
ylab("Cluster & Expert") +
scale_x_continuous(name="Q1 probability (%)",minor_breaks = seq(0, 100, 5), breaks = seq(0, 100, 10)) +
theme(legend.position = "none",axis.text=element_text(size=11)) 

}
```



## Plot Q2
```{r probintQ2, fig.width = 6, fig.height= 10}
if(origALI){
  
#The 'standard' order the WG is using is as follows: immunotoxicity, metabolic effects, neurotoxicity and developmental neurotoxicity, reproductive and developmental toxicity, and carcinogenicity and mammary gland proliferative effects. 

dfq_org <- do.call('rbind',list_df_Q2)
  dfq_org$expertnr = dfq_org$expert
  dfq_org$expert = LETTERS[dfq_org$expertnr]
dfq_org$cluexp <- paste(dfq_org$cluster,dfq_org$expert)

dfq_org$cluexp <- factor(dfq_org$cluexp,levels = dfq_org$cluexp[length(dfq_org$cluexp):1])
levels(dfq_org$cluexp)
lev1 <- levels(dfq_org$cluexp)
ord <- c(4,8,3,7,2,6,1,5, 
         11,15,10,13,9,12,14,
         17,22,16,19,21,18,20,
         28,34,27,33,26,32,25,31,24,30,23,29,
         39,44,38,43,37,42,36,41,35,40) 
lev2 <- lev1[ord]
dfq_org$cluexp <- factor(dfq_org$cluexp,levels = lev2)
dfqlower <- dfq_org
dfqlower$value <- dfq_org$lower
dfqlower$bound <- "b"
dfqupper <- dfq_org
dfqupper$value <- dfq_org$upper-dfq_org$lower
dfqupper$bound <- "a"
dfq <- rbind(dfqlower[,-c(5,6)],dfqupper[,-c(5,6)])
hline <- c(8.5,15.5,22.5,34.5)
#hline <- hline[2:4]
#dfq$nr <- nrow(dfq):1
xa = seq(-1,8,by=2)
dfq %>% 
ggplot(aes(y = cluexp, x = value, fill=bound)) +
geom_bar(position="stack",stat="identity",width = 0.5) +
theme_bw() +
scale_fill_manual(values=c("gray","NA")) +
  geom_hline(yintercept = hline,col='black')+
ylab("Cluster & Expert") +
scale_x_continuous(name="Estimated lowest BMD in this cluster \n (HED, ng BPA/kg bw per day)", breaks=xa, labels=10^xa) +
theme(legend.position = "none",axis.text=element_text(size=11)) 

}
```


# Derive lowest BMD across clusters by assessing the probability of at least one effect over the dose range

```{r}
get_p <- function(one_dose,loo='none',p_param=TRUE){

if(p_param){
p_i <- get_env(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_hocs[[1]])
p_m <- get_env(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_hocs[[2]])
p_n <- get_env(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_hocs[[3]])
p_r <- get_env(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_hocs[[4]])
p_c <- get_env(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_hocs[[5]])
}else{
p_i <- get_env(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[1]])
p_m <- get_env(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[2]])
p_n <- get_env(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[3]])
p_r <- get_env(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[4]])
p_c <- get_env(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_histo_hocs[[5]])
}

return(list(lower=1 - prod(1-p_c$lower_cdf)*
prod(1-p_i$lower_cdf)*
prod(1-p_m$lower_cdf)*
prod(1-p_n$lower_cdf)*
prod(1-p_r$lower_cdf),
upper = 1 - prod(1-p_c$upper_cdf)*
prod(1-p_i$upper_cdf)*
prod(1-p_m$upper_cdf)*
prod(1-p_n$upper_cdf)*
prod(1-p_r$upper_cdf)))
}
```


# Derive the envelope of the probability of at least one 

## parametric 

```{r}
dose = seq(-4,4,length.out = 200)

lowup_all <- lapply(1:length(dose),function(di){
  get_p(dose[di])
  })

df_env_all <- data.frame(lower_cdf=unlist(lapply(lowup_all,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all,function(x){x$upper})),dose = dose)
```

## histogram 

```{r}
lowup_all_histo <- lapply(1:length(dose),function(di){get_p(dose[di],p_param = FALSE)})

df_env_all_histo <- data.frame(lower_cdf=unlist(lapply(lowup_all_histo,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all_histo,function(x){x$upper})),dose = dose)
```

# Find 5th percentile by optimisation 

## parametric

```{r}

objective1 <- function(d){(get_p(d)$lower-0.05)^2}

objective2 <- function(d){(get_p(d)$upper-0.05)^2}

df_opt <- data.frame(lower = optimize(objective2,interval = c(-10,10))$minimum,
                     upper = optimize(objective1,interval = c(-10,10))$minimum,
cdf = 0.05,mind = min(df_env_all$dose))

```


## histogram
```{r}

objective1 <- function(d){(get_p(d,p_param=FALSE)$lower-0.05)^2}

objective2 <- function(d){(get_p(d,p_param=FALSE)$upper-0.05)^2}

df_opt_histo <- data.frame(lower = optimize(objective2,interval = c(-10,10))$minimum,
                     upper = optimize(objective1,interval = c(-10,10))$minimum,
cdf = 0.05,mind = min(df_env_all$dose))

```

```{r}
if(FALSE){
ggplot(data=df_env_all,aes(x=dose,y=100*lower_cdf)) +
  geom_line(col="black")+
  geom_line(aes(x=dose,y=100*upper_cdf),col="black")+
  geom_segment(data=df_opt,aes(x=mind,xend=lower,y=100*cdf,yend=100*cdf),col='blue')+
  geom_segment(data=df_opt,aes(x=lower,xend=upper,y=100*cdf,yend=100*cdf),col='blue',linetype='dashed')+
  geom_segment(data=df_opt,aes(x=lower,xend=lower,y=0,yend=100*cdf),col='darkred')+
  geom_segment(data=df_opt,aes(x=upper,xend=upper,y=0,yend=100*cdf),col='darkred')+
  geom_text(x=df_opt$upper+1, y=100*df_opt$cdf, label=paste0('(10^',round(df_opt$lower,2),', 10^',round(df_opt$upper,2),')'),col='darkred') +
  geom_text(x=df_opt$mind, y=100*df_opt$cdf, label="5%",col='blue') +
theme_bw()+
  ylim(c(0,100)) + 
  ggtitle("Uncertainty in estimated lowest BMD across clusters",subtitle = "envelope considering differences between experts") +
  ylab("Cumulative probability (%)") +
scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)",breaks=breaks, labels=breaks,limits = NULL)
}
```

# Plot all envelopes of clusters and the combination in the same graph

```{r}
plot_envs <- function(df_env,df_env_all=df_env_all){
df2 <- data.frame(cdf = 100*c(df_env$lower_cdf,df_env$upper_cdf),
           bound = rep(c('lower','upper'),each=length(df_env$lower_cdf)),
           dose=rep(df_env$dose,2),cluster=rep(df_env$cluster,2))
df2_all <- data.frame(cdf=100*c(df_env_all$lower_cdf,df_env_all$upper_cdf),bound=rep(c('lower','upper'),each=length(df_env_all$lower_cdf)),
                      dose=rep(df_env_all$dose,2),cluster="all")

ggplot(data=df2,aes(x=dose,y=cdf,col=cluster)) +
  geom_line()+
 #geom_line(aes(x=dose,y=upper_cdf))+
 geom_line(data=df2_all,aes(x=dose,y=cdf),col="black")+
#  geom_line(data=df_env_all,aes(x=dose,y=upper_cdf),col="black")+
theme_bw()+
  facet_wrap(~bound,ncol=2)+
  scale_x_continuous(name="Estimated lowest BMD across all cluster \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks) +
ylab("Cumulative probability (%)")+
  theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7))


}
```

## parametric
```{r lowerupper_allclusters, fig.width = 6, fig.height = 6}
plot_envs(rbind(do.call('rbind',list_env_hocs[[1]]),
                do.call('rbind',list_env_hocs[[2]]),
                do.call('rbind',list_env_hocs[[3]]),
                do.call('rbind',list_env_hocs[[4]]),
                do.call('rbind',list_env_hocs[[5]])),df_env_all = df_env_all)


```


```{r}
if(FALSE){
plot_envs(rbind(do.call('rbind',list_env_hocs[[1]]),
                do.call('rbind',list_env_hocs[[2]]),
                do.call('rbind',list_env_hocs[[3]]),
                do.call('rbind',list_env_hocs[[4]]),
                do.call('rbind',list_env_hocs[[5]])),df_env_all = df_env_all_noALI)
}
```

# Plot envelope with and without allergic lung inflammation 

```{r}
clid_remove = 1
lowup_all <- lapply(1:length(dose),function(di){get_p(dose[di],loo=clusters[clid_remove])})

df_env_all_noALI <- data.frame(lower_cdf=unlist(lapply(lowup_all,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all,function(x){x$upper})),dose = dose)

objective1 <- function(d){(get_p(d,loo=clusters[clid_remove])$lower-0.05)^2}

objective2 <- function(d){(get_p(d,loo=clusters[clid_remove])$upper-0.05)^2}

df_opt_noALI <- data.frame(lower = optimize(objective2,interval = c(-10,10))$minimum,
                     upper = optimize(objective1,interval = c(-10,10))$minimum,
cdf = 0.05,mind = min(df_env_all_noALI$dose))

```

```{r env}
df_opt1 <- data.frame(df_opt)
df_opt1$limit = df_opt$upper
df_opt1$lower = df_opt_noALI$lower
df_opt1$upper = df_opt_noALI$upper
df_opt$limit = limits[1]
ggplot(data=df_env_all,aes(x=dose,y=100*lower_cdf)) +
  geom_line(col="black")+
  geom_line(aes(x=dose,y=100*upper_cdf),col="black")+
  geom_line(data=df_env_all_noALI,aes(x=dose,y=100*upper_cdf),col="black",linetype='dashed')+
  geom_line(data=df_env_all_noALI,aes(x=dose,y=100*lower_cdf),col="black",linetype='dashed')+
theme_bw()+
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)
```

Plot parametric and histogram 

```{r paramhisto}
df_env_all$distribution = 'parametric'
df_env_all_histo$distribution = 'histogram'
df_ph <- rbind(df_env_all,df_env_all_histo)

ggplot(data=df_ph,aes(x=dose,y=100*lower_cdf,col = distribution)) +
  scale_color_manual(values = c('black','darkred'))+
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf)) + 
  geom_hline(yintercept = 0.05*100,col='blue') +
theme_bw() + 
  theme(legend.position = "none")+
  ylab("Cumulative probability (%)") +
  #theme(legend.position="bottom",legend.title = element_text(size=8),
  #    legend.text = element_text(size=7)) +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = NULL)
```

# Calculate envelopes for different choices of percentiles

## parameteric 

```{r}
perc = c(0.01,0.025,seq(0.05,0.95,by=0.05))
df_calc_perc <- do.call('rbind',lapply(1:length(perc),function(ip){
objective1 <- function(d){(get_p(d)$lower-perc[ip])^2}

objective2 <- function(d){(get_p(d)$upper-perc[ip])^2}

df_opt <- data.frame(perc = perc[ip],
lower = optimize(objective2,interval = c(-10,10))$minimum,
upper = optimize(objective1,interval = c(-10,10))$minimum)
}))

#write.xlsx(df_calc_perc,file=paste('calculated_percentiles_BPA',probmassoutside,origALI,'.xlsx'))

```

## histogram 

```{r}
df_calc_perc <- do.call('rbind',lapply(1:length(perc),function(ip){
objective1 <- function(d){(get_p(d,p_param=FALSE)$lower-perc[ip])^2}

objective2 <- function(d){(get_p(d,p_param=FALSE)$upper-perc[ip])^2}

df_opt <- data.frame(perc = perc[ip],
lower = optimize(objective2,interval = c(-10,10))$minimum,
upper = optimize(objective1,interval = c(-10,10))$minimum)
}))

#write.xlsx(df_calc_perc,file=paste('calculated_percentiles_BPA_histo',probmassoutside,origALI,'.xlsx'))
```

# Plot all envelopes of clusters and the combination in the same graph

# Sensitivity analysis

## Evaluate influence on the 5th percentile of lowest BMD of clusters using leave-one-out

```{r}
clusters_all <- c('all',clusters)
sa_c <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p(d,loo=clusters_all[clid])$lower-0.05)^2}

objective2 <- function(d){(get_p(d,loo=clusters_all[clid])$upper-0.05)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = 0.05,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))
```

derive percentiles for the envelope without allergic lung inflammation 

```{r}
clid_remove = 1
perc = c(0.01,0.025,seq(0.05,0.95,by=0.05))
df_calc_perc_noALI <- do.call('rbind',lapply(1:length(perc),function(ip){
objective1 <- function(d){(get_p(d,loo=clusters[clid_remove])$lower-perc[ip])^2}

objective2 <- function(d){(get_p(d,loo=clusters[clid_remove])$upper-perc[ip])^2}

df_opt <- data.frame(perc = perc[ip],
lower = optimize(objective2,interval = c(-10,10))$minimum,
upper = optimize(objective1,interval = c(-10,10))$minimum)
}))

#write.xlsx(df_calc_perc_noALI,file=paste('calculated_percentiles_BPA',probmassoutside,origALI,'_noALI.xlsx'))
```

```{r sa,fig.width = 6, fig.height = 3}
ggplot(sa_c,aes(y=cluster,x=lower,fill=cluster))+
# geom_point() + 
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
 # xlim(-2,-1) + 
#  facet_wrap(~iter) +
  theme_bw()+
    ylab("Cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name="5th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-3,1)) 
  #ggtitle("Sensitivity analysis", subtitle="Leave-one-out")

```


## Evaluate influence on the 5th percentile of lowest BMD of clusters using leave-one-out (when the most influential has been removed)

```{r}
clid_remove = 1
clusters_all <- c('all',clusters[-clid_remove])
sa_c2 <- do.call('rbind',lapply(1:length(clusters_all),function(clid){
objective1 <- function(d){(get_p(d,loo=c(clusters[clid_remove],clusters_all[clid]))$lower-0.05)^2}

objective2 <- function(d){(get_p(d,loo=c(clusters[clid_remove],clusters_all[clid]))$upper-0.05)^2}

df_opt <- data.frame(lower = optimize(objective1,interval = c(-10,10))$minimum,
upper = optimize(objective2,interval = c(-10,10))$minimum,cdf = 0.05,mind = min(df_env_all$dose),cluster = clusters_all[clid])
}))

```

```{r sa_withoutALI,fig.width = 6, fig.height = 3}
ggplot(sa_c2,aes(y=cluster,x=lower,fill=cluster))+
# geom_point() + 
  geom_errorbarh(aes(xmin = lower,xmax = upper,col=cluster))+
 # xlim(-2,-1) + 
#  facet_wrap(~iter) +
  theme_bw()+
  ylab("Cluster omitted") +
  theme(legend.position = "none") +
  scale_x_continuous(name="5th percentile for estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = c(-3,1)) 
  #ggtitle("Sensitivity analysis without Allergic lung inflammation", subtitle="Leave-one-out")
```

# Sensitivity analysis - consider possible dependencies between clusters 

```{r}
get_p_with_dependencies <- function(one_dose,loo='none',dep,rho){

p_i <- get_env(info_hocs[[1]][!(info_hocs[[1]]$cluster %in% loo),],one_dose,pfunctions_hocs[[1]])
p_m <- get_env(info_hocs[[2]][!(info_hocs[[2]]$cluster %in% loo),],one_dose,pfunctions_hocs[[2]])
p_n <- get_env(info_hocs[[3]][!(info_hocs[[3]]$cluster %in% loo),],one_dose,pfunctions_hocs[[3]])
p_r <- get_env(info_hocs[[4]][!(info_hocs[[4]]$cluster %in% loo),],one_dose,pfunctions_hocs[[4]])
p_c <- get_env(info_hocs[[5]][!(info_hocs[[5]]$cluster %in% loo),],one_dose,pfunctions_hocs[[5]])

# turn probabilities to 1 or zero where there are dependencies 
rbind(p_c[p_c$cluster %in% dep,1:2],
p_i[p_i$cluster %in% dep,1:2],
p_m[p_m$cluster %in% dep,1:2],
p_n[p_n$cluster %in% dep,1:2],
p_r[p_r$cluster %in% dep,1:2])

p_c[p_c$cluster %in% dep,1:2] = 0
p_i[p_i$cluster %in% dep,1:2] = 0
p_m[p_m$cluster %in% dep,1:2] = 0
p_n[p_n$cluster %in% dep,1:2] = 0
p_r[p_r$cluster %in% dep,1:2] = 0


# derive joint probability for dependent clusters 
i=as.numeric(cut(which(dep[1]==clusters),c(0,4,9,15,18,21)))
clid_i=which(unlist(lapply(list_env_hocs[[i]],function(ee){ee$cluster[1]})) %in% dep[1])
j=as.numeric(cut(which(dep[2]==clusters),c(0,4,9,15,18,21)))
clid_j=which(unlist(lapply(list_env_hocs[[j]],function(ee){ee$cluster[1]})) %in% dep[2])

jointprob = approx_jointprobability(target_d=one_dose,rho=rho,i=i,j=j,clid_i=clid_i,clid_j=clid_j,niter=15000)$probisd

return(list(lower=1 - prod(1-p_c$lower_cdf)*
prod(1-p_i$lower_cdf)*
prod(1-p_m$lower_cdf)*
prod(1-p_n$lower_cdf)*
prod(1-p_r$lower_cdf)*
  (max(jointprob)),
upper = 1 - prod(1-p_c$upper_cdf)*
prod(1-p_i$upper_cdf)*
prod(1-p_m$upper_cdf)*
prod(1-p_n$upper_cdf)*
prod(1-p_r$upper_cdf)*
  (min(jointprob))))
}
```


## Function to consider dependencies between two clusters 

```{r}
temp <- range(df_env_all$dose[df_env_all$upper_cdf>0.01 & df_env_all$lower_cdf<0.99])
dose_2 <- seq(temp[1],temp[2],length.out = 100)

get_dep <- function(clid_deps,rhos){
do.call('rbind',lapply(1:length(rhos),function(rid){
lowup_all_dep <- lapply(1:length(dose_2),function(di){get_p_with_dependencies(dose_2[di],loo='none',dep =clusters[clid_deps],rho=rhos[rid])})

data.frame(lower_cdf=unlist(lapply(lowup_all_dep,function(x){x$lower})),upper_cdf=unlist(lapply(lowup_all_dep,function(x){x$upper})),dose = dose_2,rho = rhos[rid])
}
))
}
```

Male 

```{r dep_ALI_male}
df_dep <- get_dep(clid_deps=c(1,16),rhos = c(-0.9,0,0.5,0.9))
df_dep$correlation = as.character(df_dep$rho)

ggplot(data=df_dep,aes(x=dose,y=100*lower_cdf,color = correlation)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf,color = correlation))+
geom_line(data=df_env_all,aes(x=dose,y=100*lower_cdf),col="black",alpha=0.7)+
geom_line(data=df_env_all,aes(x=dose,y=100*upper_cdf),col="black",alpha=0.7)+
theme_bw() +
  theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7)) +
  theme(plot.title = element_text(size = 8)) +
  ggtitle("Dependence between Allergic Lung Inflammation \n and Male reprotoxicity") +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED,  ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)
```

Female

```{r dep_ALI_female}
df_dep <- get_dep(clid_deps=c(1,17),rhos = c(-0.9,0,0.5,0.9))
df_dep$correlation = as.character(df_dep$rho)

ggplot(data=df_dep,aes(x=dose,y=100*lower_cdf,color = correlation)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf,color = correlation))+
geom_line(data=df_env_all,aes(x=dose,y=100*lower_cdf),col="black",alpha=0.7)+
geom_line(data=df_env_all,aes(x=dose,y=100*upper_cdf),col="black",alpha=0.7)+
theme_bw() +
  theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7)) +
  ggtitle("Dependence between Allergic Lung Inflammation \n and Female reprotoxicity") +
  theme(plot.title = element_text(size = 8)) +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estiamted lowest BMD across all clusters \n (HED,  ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)
```

Male vs Female

```{r dep_male_female}
df_dep <- get_dep(clid_deps=c(16,17),rhos = c(-0.9,0,0.5,0.9))
df_dep$correlation = as.character(df_dep$rho)

ggplot(data=df_dep,aes(x=dose,y=100*lower_cdf,color = correlation)) +
  geom_line()+
  geom_line(aes(x=dose,y=100*upper_cdf,color = correlation))+
geom_line(data=df_env_all,aes(x=dose,y=100*lower_cdf),col="black",alpha=0.7)+
geom_line(data=df_env_all,aes(x=dose,y=100*upper_cdf),col="black",alpha=0.7)+
theme_bw() +
 theme(legend.position="bottom",legend.title = element_text(size=8),
      legend.text = element_text(size=7)) +
   ggtitle("Dependence between Male and \n Female reprotoxicity") +
theme(plot.title = element_text(size = 8)) +
  ylab("Cumulative probability (%)") +
  scale_x_continuous(name="Estimated lowest BMD across all clusters \n (HED, ng BPA/kg bw per day)", breaks=breaks, labels=10^breaks,limits = limits)
```


